Article title

### 2018-11-08 docs/rupee.tex
paper

>>>>

Not to understate the significance of what has been shown, that a purely geometric sequence alignment-free big data approach to protein structure search can compete with the current state of the art protein structure searches available, there remains challenges for RUPEE to address in addition to avenues for further investigation.

While our min-hashing and LSH scheme does allow for some flexibility in the size of matched protein structures, it is not specifically designed for containment searches. 
However, the initial min-hashing and LSH search does operate fast enough, within seconds, that it does present the possibility of executing multiple searches. 
With more resources, we can distribute min-hash and band data across multiple compute units, with each data set representing a subset of chopped domain representations. 
With a 75\% overlap of these subsets, RUPEE searches effectively become containment searches.

We have tried the overlapping subset idea and have found it to be effective. 
However, on a single compute unit, the time required is more than we are willing to accept for this first iteration of RUPEE.

One possible drawback of RUPEE is that in both fast and top-aligned modes, it only returns the top 400 results. 
Again, with more resources, this number can be increased, but there still remains a need for a cut-off.

In most search domains, having to looking past the first few hundred results usually indicates an ineffective search strategy.
For instance, RUPEE provides filters that can be used for traversing structure space more efficiently. 
For SCOPe, CATH, and ECOD you can instruct the search to only return domains that differ from the query domain at a chosen hierarchy level classification. 
Additionally, for CATH you can filter results based on hierarchy level representatives. 
Since RUPEE does not rely on sequence clusters, these kinds of filters are easy to implement, do not reduce the number of returned results, and allow for the discovery of unexpected structural similarities across classification hierarchies.

One area that stands out for possible improvement is our longest common subsequence (LCS) scoring adjustment to the results initially returned by RUPEE. 
While the LCS step has been shown to be effective, it is notable for its simplicity. 
A more complex step of validating the sequence of gram matches can take a form similar to the path extension algorithm used by CE. 
In this case, sequences of matches would only be extended when the difference of interresidue distances between gram pairs already in the sequence and a candidate pair to be added to the sequence fall below some threshold.

On the other hand, it would be interesting to see where further analysis of the initial results returned by RUPEE before LCS and any sort of order enforcement beyond that of the grams themselves could lead. 
Sin

As can be observed from Figure 4 and Figure 5, there are good domain matches with the SCOP hierarchy that mTM is able to find that RUPEE does not. 
Conversely, there are good domain matches outside not aligned with the SCOP hierarchy that RUPEE finds and mTM is not. 
A comprehensive listing of these difference may find interesting similarities not previously known.
